Verifying Demonstrations

### 2021-06-17 paper/performance.tex

As above, assume we have one trusted witness.
A smartphone ran Idemix in \SI{153}{\milli\second} back in 2014.
3DB-access~\cite{3db-access} says their distance-bounding part takes less than 
\SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
maximum \SI{200}{\metre}).
Then a witness fixed in one position can cover \SI{45216}{\square\metre} 
(\SI{120}{\metre} radius), which fits 137018~protesters according to 
\textcite{2016DemonstrationsInSeoul}.
It would take this witness \SI{5.8}{\hour} to witness all of them.
Thus, to witness 1\,000\,000 protesters, it would take \SI{8}{\hour} for 5.3 
witnesses.

>>>>

As above, assume we have one trusted witness.
A smartphone ran Idemix in \SI{153}{\milli\second} back in 2014.
3DB-access~\cite{3db-access} says their distance-bounding part takes less than 
\SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
maximum \SI{200}{\metre})\footnote{%
  These numbers are representative of what \textcite{DB-Schnorr} use for 
  underlying communication technology.
}.
Then a witness fixed in one position can cover \SI{45216}{\square\metre} 
(\SI{120}{\metre} radius), which fits 137018~protesters according to 
\textcite{2016DemonstrationsInSeoul}.
It would take this witness \SI{5.8}{\hour} to witness all of them.
Thus, to witness 1\,000\,000 protesters, it would take \SI{8}{\hour} for 5.3 
witnesses.
